---
title: "Milestone 4"
author: "Saul Soto"
date: "3/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(spotifyr)
library(lubridate)
library(readxl)
library(janitor)
library(rvest)
library(infer)
library(magrittr)
library(hrbrthemes)
library(extrafont)
library(gganimate)
library(transformr)
library(gt)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
library(tm)
Sys.setenv(SPOTIFY_CLIENT_ID = '1ebacb60ef2044ccadab18602f7c0b8f')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '6fb54464f8dc45c88387a4fadde775db')

access_token <- get_spotify_access_token()

# So it turns out that I am completely unable to get any data from Germany or
# the UK because I have a USA Spotify account. What I will do for this milestone
# is get the spotify top 200 tracks for the past 3 Februarys (Spotify only has
# data up until 2017) and store them in their own dataframe (UK and Germany).
# Since the dataframes do not give me details about the genre or any analysis,
# that means I'll have to do it individually for every song, which is a little
# absurd given the time for this project. My plan is to hopefully get Spotify to
# give me access to the global market, if not I will narrow my project.


```



```{r charts_data, echo=FALSE}
# I added this because I thought it would fix the problem with spotify returning
# NULL observations, but it did not :(

options(stringsAsFactors = FALSE)

# Thank you Mitchell for the lines of code below!!

uk2000_hits <- "http://www.uk-charts.top-source.info/top-100-2000.shtml" %>%
  read_html()

uk_2000_data <- html_nodes(uk2000_hits, "td") %>% 
  html_text()

# Okay so contrary to my belief, rep will not be the best way to split the list
# up, but the as.data.frame function will automatically continue to split the
# first three rows into a separate column. Perhaps there is another way to do
# this, but I like this method for now.

uk_2000_data <- as.data.frame(split(uk_2000_data, 1:3)) %>% 
  rename(position = X1,
         artist = X2,
         title = X3)

# Here I read in UK charts data from the website, convert it into html_text
# dataframe, then clean up the data so it lists the position, artist, and title
# of the song.

uk2001_hits <- "http://www.uk-charts.top-source.info/top-100-2001.shtml" %>%
  read_html()

uk2001_hits <- html_nodes(uk2001_hits, "td") %>%
  html_text()

uk2001_data <- as.data.frame(split(uk2001_hits, 1:3)) %>% 
  rename(position = X1,
         artist = X2,
         title = X3)

uk2002_hits <- "http://www.uk-charts.top-source.info/top-100-2002.shtml" %>%
  read_html()

uk2002_hits <- html_nodes(uk2002_hits, "td") %>%
  html_text()

uk2002_data <- as.data.frame(split(uk2002_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2003_hits <- "http://www.uk-charts.top-source.info/top-100-2003.shtml" %>%
  read_html()

uk2003_hits <- html_nodes(uk2003_hits, "td") %>%
  html_text()

uk2003_data <- as.data.frame(split(uk2003_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2004_hits <- "http://www.uk-charts.top-source.info/top-100-2004.shtml" %>%
  read_html()

uk2004_hits <- html_nodes(uk2004_hits, "td") %>%
  html_text()

uk2004_data <- as.data.frame(split(uk2004_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2005_hits <- "http://www.uk-charts.top-source.info/top-100-2005.shtml" %>%
  read_html()

uk2005_hits <- html_nodes(uk2005_hits, "td") %>%
  html_text()

uk2005_data <- as.data.frame(split(uk2005_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2006_hits <- "http://www.uk-charts.top-source.info/top-100-2006.shtml" %>%
  read_html()

uk2006_hits <- html_nodes(uk2006_hits, "td") %>%
  html_text()

uk2006_data <- as.data.frame(split(uk2006_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2007_hits <- "http://www.uk-charts.top-source.info/top-100-2007.shtml" %>%
  read_html()

uk2007_hits <- html_nodes(uk2007_hits, "td") %>%
  html_text()

uk2007_data <- as.data.frame(split(uk2007_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2008_hits <- "http://www.uk-charts.top-source.info/top-100-2008.shtml" %>%
  read_html()

uk2008_hits <- html_nodes(uk2008_hits, "td") %>%
  html_text()

uk2008_data <- as.data.frame(split(uk2008_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2009_hits <- "http://www.uk-charts.top-source.info/top-100-2009.shtml" %>%
  read_html()

uk2009_hits <- html_nodes(uk2009_hits, "td") %>%
  html_text()

uk2009_data <- as.data.frame(split(uk2009_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

uk2010_hits <- "http://www.uk-charts.top-source.info/top-100-2010.shtml" %>%
  read_html()

uk2010_hits <- html_nodes(uk2010_hits, "td") %>%
  html_text()

uk2010_data <- as.data.frame(split(uk2010_hits, 1:3)) %>%
  rename(position = X1,
         artist = X2,
         title = X3)

# I do the same for the Germany data below. Note, I had to do a little extra
# more steps because the Offizielle Deutsche Charts website displayed their data
# in a rather peculiar way, creating a VERY ugly looking dataset when I read it
# in as html.

ger2000_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2000" %>%
  read_html()

# For example, here (thanks to Mitchell!) I converted the data to html text
# format, then I had to get rid of the extra spaces that occurred after
# converting to text. I then created a tibble for the almost cleaned up germany
# charts data.

ger2000_hits <- html_nodes(ger2000_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("\\n+", "")%>%
  trimws()%>%
  tibble()

# Here, I renamed the column that had both the artists and the song and then
# split the artist and song title into separate columns. Note: there were 36
# spaces in between the artist name and the song title which is why I had to use
# string split again.

colnames(ger2000_hits)<-c("Column")

ger2000_hits<- ger2000_hits %>% 
  mutate(Names=str_split(Column,"\\s{36}"))

# Finally, I organize the german data once more and have artist and song title
# in separate columns. Unfortunately, the germany dataset did not come with a
# position column, however I did not add it because I can just look at what row
# number the song falls under to know it's position in the charts.

ger2000_data <- data.frame(matrix(unlist(ger2000_hits$Names),
                                  nrow=100, byrow=T),stringsAsFactors=FALSE)

ger2001_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2001" %>%
  read_html()

ger2001_hits <- html_nodes(ger2001_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2001_hits)<-c("Column")

ger2001_hits <- ger2001_hits %>%
  mutate(Names=str_split(Column, "\\s{36}"))

ger2001_data <- data.frame(matrix(unlist(ger2001_hits$Names),
                                  nrow=100,
                                  byrow = T),
                           stringsAsFactors = FALSE)

ger2002_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2002" %>%
  read_html()

ger2002_hits <- html_nodes(ger2002_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2002_hits)<-c("Column")

ger2002_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2002_data <- data.frame(matrix(unlist(ger2002_hits$Names),
                                  nrow=100,
                                  byrow = T),
                           stringsAsFactors = FALSE)

ger2003_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2003" %>%
  read_html()

ger2003_hits <- html_nodes(ger2003_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2003_hits)<-c("Column")

ger2003_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2003_data <- data.frame(matrix(unlist(ger2003_hits$Names),
                                  nrow=100,
                                  byrow = T),
                           stringsAsFactors = FALSE)

ger2004_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2004" %>%
  read_html()

ger2004_hits <- html_nodes(ger2004_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2004_hits)<-c("Column")

ger2004_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2004_data <- data.frame(matrix(unlist(ger2004_hits$Names),
                                  nrow=100,
                                  byrow = T),
                           stringsAsFactors = FALSE)

ger2005_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2005" %>%
  read_html()

ger2005_hits <- html_nodes(ger2005_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2005_hits)<-c("Column")

ger2005_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2005_data <- data.frame(matrix(unlist(ger2005_hits$Names),
                                  nrow=100,
                                  byrow = T),
                           stringsAsFactors = FALSE)

ger2006_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2006" %>%
  read_html()

ger2006_hits <- html_nodes(ger2006_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2006_hits)<-c("Column")

ger2006_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2006_data <- data.frame(matrix(unlist(ger2006_hits$Names),
                                  nrow=100,
                                  byrow = T),
                           stringsAsFactors = FALSE)

ger2007_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2007" %>%
  read_html()

ger2007_hits <- html_nodes(ger2007_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2007_hits)<-c("Column")

ger2007_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2007_data <- data.frame(matrix(unlist(ger2007_hits$Names),
                                  nrow=100,
                                  byrow = T), stringsAsFactors = FALSE)

ger2008_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2008" %>%
  read_html()

ger2008_hits <- html_nodes(ger2008_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2008_hits)<-c("Column")

ger2008_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2008_data <- data.frame(matrix(unlist(ger2008_hits$Names),
                                  nrow=100,
                                  byrow = T), stringsAsFactors = FALSE)

ger2009_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2009" %>%
  read_html()

ger2009_hits <- html_nodes(ger2009_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2009_hits)<-c("Column")

ger2009_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2009_data <- data.frame(matrix(unlist(ger2009_hits$Names),
                                  nrow=100,
                                  byrow = T), stringsAsFactors = FALSE)

ger2010_hits <- "https://www.offiziellecharts.de/charts/single-jahr/for-date-2010" %>%
  read_html()

ger2010_hits <- html_nodes(ger2010_hits, ".year-mode") %>%
  html_text() %>%
  str_replace_all("//n+", "") %>%
  trimws() %>%
  tibble()

colnames(ger2010_hits)<-c("Column")

ger2010_hits %<>% mutate(Names=str_split(Column, "\\s{36}"))

ger2010_data <- data.frame(matrix(unlist(ger2010_hits$Names),
                                  nrow=100,
                                  byrow = T), stringsAsFactors = FALSE)

# Here I will get the audio features for every year in both UK and Germany.

# This is how I gathered the audio features data. First, I created 22 playlists,
# each dedicated to a year in the charts for the UK and Germany. I have one
# playlist for the UK 2000 Charts and so on. Then, I read in the playlist
# information into a variable. Afterwards, I get the track information from the
# playlists, and use that to get the audio analysis features (danceability,
# energy, tempo, etc.) needed for my shiny app.

uk_2000 <- get_playlist("7uQBCcnNuxOBv0jFbEcYjH")
uk2000_tracks <- get_playlist_tracks("7uQBCcnNuxOBv0jFbEcYjH") 
uk2000_features <- get_track_audio_features(uk2000_tracks$track.id)

uk_2001 <- get_playlist("28MXvLEP4jZ6c5kVIP8ke5")
uk2001_tracks <- get_playlist_tracks("28MXvLEP4jZ6c5kVIP8ke5")
uk2001_features <- get_track_audio_features(uk2001_tracks$track.id)

uk2002 <- get_playlist("7vQW2yhyPeUys745cjd4qW")
uk2002_tracks <- get_playlist_tracks("7vQW2yhyPeUys745cjd4qW")
uk2002_features <- get_track_audio_features(uk2002_tracks$track.id)

uk2003 <- get_playlist("7ajCdWcuELFirRcGl9LKsv")
uk2003_tracks <- get_playlist_tracks("7ajCdWcuELFirRcGl9LKsv")
uk2003_features <- get_track_audio_features(uk2003_tracks$track.id)

uk2004 <- get_playlist("4d9CrfTDJ7WgDXL7xy4gnu")
uk2004_tracks <- get_playlist_tracks("4d9CrfTDJ7WgDXL7xy4gnu")
uk2004_features <- get_track_audio_features(uk2004_tracks$track.id)

uk2005 <- get_playlist("2luAWE5y4EjcF3eeecXqqL")
uk2005_tracks <- get_playlist_tracks("2luAWE5y4EjcF3eeecXqqL")
uk2005_features <- get_track_audio_features(uk2005_tracks$track.id)

uk2006 <- get_playlist("246jBtzSV8noLKfwPhxK9L")
uk2006_tracks <- get_playlist_tracks("246jBtzSV8noLKfwPhxK9L")
uk2006_features <- get_track_audio_features(uk2006_tracks$track.id)

uk2007 <- get_playlist("41tjYI2R4zuKCR6Jpkcurs")
uk2007_tracks <- get_playlist_tracks("41tjYI2R4zuKCR6Jpkcurs")
uk2007_features <- get_track_audio_features(uk2007_tracks$track.id)

uk2008 <- get_playlist("2e6HTZLlouOqvX2hFfrK7M")
uk2008_tracks <- get_playlist_tracks("2e6HTZLlouOqvX2hFfrK7M")
uk2008_features <- get_track_audio_features(uk2008_tracks$track.id)

uk2009 <- get_playlist("36Wp100hDpZ39S7rAkeW2B")
uk2009_tracks <- get_playlist_tracks("36Wp100hDpZ39S7rAkeW2B")
uk2009_features <- get_track_audio_features(uk2009_tracks$track.id)

uk2010 <- get_playlist("1oFHWJu7rH78TBCxbUvLne")
uk2010_tracks <- get_playlist_tracks("1oFHWJu7rH78TBCxbUvLne")
uk2010_features <- get_track_audio_features(uk2010_tracks$track.id)

ger2000 <- get_playlist("3mwXtmIDVIImnHEhF25aXk")
ger2000_tracks <- get_playlist_tracks("3mwXtmIDVIImnHEhF25aXk")
ger2000_features <- get_track_audio_features(ger2000_tracks$track.id)

ger2001 <- get_playlist("5Xl6JK20GTICxAQsMjrp93")
ger2001_tracks <- get_playlist_tracks("5Xl6JK20GTICxAQsMjrp93")
ger2001_features <- get_track_audio_features(ger2001_tracks$track.id)

ger2002 <- get_playlist("4pN5sDpaQn5pGVJQJ8Nm7j")
ger2002_tracks <- get_playlist_tracks("4pN5sDpaQn5pGVJQJ8Nm7j")
ger2002_features <- get_track_audio_features(ger2002_tracks$track.id)

ger2003 <- get_playlist("4CfPTjH2UOLZr3FjtbmnPB")
ger2003_tracks <- get_playlist_tracks("4CfPTjH2UOLZr3FjtbmnPB")
ger2003_features <- get_track_audio_features(ger2003_tracks$track.id)

ger2004 <- get_playlist("6RsriY4UcnhHpKNoeVYbu4")
ger2004_tracks <- get_playlist_tracks("6RsriY4UcnhHpKNoeVYbu4")
ger2004_features <- get_track_audio_features(ger2004_tracks$track.id)

ger2005 <- get_playlist("2nfm7TsAcuHr7p1MrOFKcw")
ger2005_tracks <- get_playlist_tracks("2nfm7TsAcuHr7p1MrOFKcw")
ger2005_features <- get_track_audio_features(ger2005_tracks$track.id)

ger2006 <- get_playlist("77N8qjXKrsVVMv8hI8jNxG")
ger2006_tracks <- get_playlist_tracks("77N8qjXKrsVVMv8hI8jNxG")
ger2006_features <- get_track_audio_features(ger2006_tracks$track.id)

ger2007 <- get_playlist("4mwHWiCKwzdIx3ANL19vRY")
ger2007_tracks <- get_playlist_tracks("4mwHWiCKwzdIx3ANL19vRY")
ger2007_features <- get_track_audio_features(ger2007_tracks$track.id)

ger2008 <- get_playlist("3o5sU5OWHsFsbh9FXjYQKE")
ger2008_tracks <- get_playlist_tracks("3o5sU5OWHsFsbh9FXjYQKE")
ger2008_features <- get_track_audio_features(ger2008_tracks$track.id)

ger2009 <- get_playlist("1teQpbhtQztADlDeANRwUs")
ger2009_tracks <- get_playlist_tracks("1teQpbhtQztADlDeANRwUs")
ger2009_features <- get_track_audio_features(ger2009_tracks$track.id)

ger2010 <- get_playlist("1RZV5fBYJUEfeYbT9kiDnk")
ger2010_tracks <- get_playlist_tracks("1RZV5fBYJUEfeYbT9kiDnk")
ger2010_features <- get_track_audio_features(ger2010_tracks$track.id)
```


```{r get_genre_data, echo=FALSE}
# What function should do: Get the genres from each song. Then, I would use a
# map function and paste the genres onto a new column in the uk2000_genre df.

# What this function does, stores the song ID into a variable, then gets the
# artist info and the genre info for that song, creating a new column in the
# original dataset. The function then returns the modified dataframe back.

get_genre <- function(df) {
  for(i in 1:nrow(df)) {
    SongID <- df$track.artist[[i]][[2]]
    SongGenre <- get_artist(SongID[1])
    df$genre[i] <- paste(unlist(SongGenre[["genres"]]),
                                  sep="", collapse=",")
  }
  df
}

# Here I use the get_genre function to add a genre column to every UK and
# Germany Charts data. This process takes a very long time, so I created a new r
# chunk with cache turned on.

uk2000_tracks %<>%
  get_genre()
uk2001_tracks %<>%
  get_genre()
uk2002_tracks %<>%
  get_genre()
uk2003_tracks %<>%
  get_genre()
uk2004_tracks %<>%
  get_genre()
uk2005_tracks %<>%
  get_genre()
uk2006_tracks %<>%
  get_genre()
uk2007_tracks %<>%
  get_genre()
uk2008_tracks %<>%
  get_genre()
uk2009_tracks %<>%
  get_genre()
uk2010_tracks %<>%
  get_genre()
ger2000_tracks %<>%
  get_genre()
ger2001_tracks %<>%
  get_genre()
ger2002_tracks %<>%
  get_genre()
ger2003_tracks %<>%
  get_genre()
ger2004_tracks %<>%
  get_genre()
ger2005_tracks %<>%
  get_genre()
ger2006_tracks %<>%
  get_genre()
ger2007_tracks %<>%
  get_genre()
ger2008_tracks %<>%
  get_genre()
ger2009_tracks %<>%
  get_genre()
ger2010_tracks %<>%
  get_genre()
```


```{r chart_analysis, echo=FALSE}
# Cleaning up the UK data, creating a year and position variable so I can
# combine everything into one huge dataset.

uk2000_tracks %<>%
  mutate(year = 2000,
         position = 1:nrow(.))
uk2001_tracks %<>%
  mutate(year = 2001,
         position = 1:nrow(.))
uk2002_tracks %<>%
  mutate(year = 2002,
         position = 1:nrow(.))
uk2003_tracks %<>%
  mutate(year = 2003,
         position = 1:nrow(.))
uk2004_tracks %<>%
  mutate(year = 2004,
         position = 1:nrow(.))
uk2005_tracks %<>%
  mutate(year = 2005,
         position = 1:nrow(.))
uk2006_tracks %<>%
  mutate(year = 2006,
         position = 1:nrow(.))
uk2007_tracks %<>%
  mutate(year = 2007,
         position = 1:nrow(.))
uk2008_tracks %<>%
  mutate(year = 2008,
         position = 1:nrow(.))
uk2009_tracks %<>%
  mutate(year = 2009,
         position = 1:nrow(.))
uk2010_tracks %<>%
  mutate(year = 2010,
         position = 1:nrow(.))

ger2000_tracks %<>%
  mutate(year = 2000,
         position = 1:nrow(.))
ger2001_tracks %<>%
  mutate(year = 2001,
         position = 1:nrow(.))
ger2002_tracks %<>%
  mutate(year = 2002,
         position = 1:nrow(.))
ger2003_tracks %<>%
  mutate(year = 2003,
         position = 1:nrow(.))
ger2004_tracks %<>%
  mutate(year = 2004,
         position = 1:nrow(.))
ger2005_tracks %<>%
  mutate(year = 2005,
         position = 1:nrow(.))
ger2006_tracks %<>%
  mutate(year = 2006,
         position = 1:nrow(.))
ger2007_tracks %<>%
  mutate(year = 2007,
         position = 1:nrow(.))
ger2008_tracks %<>%
  mutate(year = 2008,
         position = 1:nrow(.))
ger2009_tracks %<>%
  mutate(year = 2009,
         position = 1:nrow(.))
ger2010_tracks %<>%
  mutate(year = 2010,
         position = 1:nrow(.))

# Here, I create the UK and Germany charts data so I can refer to this in the
# shiny app. This will allow me to look at the whole dataset and make decade
# comparisons :)

uk_charts <- rbind(uk2000_tracks,
                   uk2001_tracks,
                   uk2002_tracks,
                   uk2003_tracks,
                   uk2004_tracks,
                   uk2005_tracks,
                   uk2006_tracks,
                   uk2007_tracks,
                   uk2008_tracks,
                   uk2009_tracks,
                   uk2010_tracks)

ger_charts <- rbind(ger2000_tracks,
                    ger2001_tracks,
                    ger2002_tracks,
                    ger2003_tracks,
                    ger2004_tracks,
                    ger2005_tracks,
                    ger2006_tracks,
                    ger2007_tracks,
                    ger2008_tracks,
                    ger2009_tracks,
                    ger2010_tracks)

# I create a massive dataframe for the UK/GER features so I can combine them and
# look at not only the track information from the playlists, but also the audio
# features analysis. It was not a problem combining these two datasets because
# they get their info from the same place (the Spotify playlists I created) and
# thus have the same amount of observations.

uk_features <- rbind(uk2000_features,
                     uk2001_features,
                     uk2002_features,
                     uk2003_features,
                     uk2004_features,
                     uk2005_features,
                     uk2006_features,
                     uk2007_features,
                     uk2008_features,
                     uk2009_features,
                     uk2010_features)

uk_charts <- cbind(uk_charts,
                   uk_features)

ger_features <- rbind(ger2000_features,
                      ger2001_features,
                      ger2002_features,
                      ger2003_features,
                      ger2004_features,
                      ger2005_features,
                      ger2006_features,
                      ger2007_features,
                      ger2008_features,
                      ger2009_features,
                      ger2010_features)

ger_charts <- cbind(ger_charts,
                    ger_features)

# I saved the data here so I would later use it for the ShinyApp, but I changed
# my code so the following chunk below is NULL. Something I did learn about
# saving RDS files and reading them on shiny is that I have to make sure I save
# them in the folder where the shiny app is or else it won't be able to find the
# data.

# saveRDS(uk_charts, file = "uk_charts")
# saveRDS(ger_charts, file = "ger_charts")

# Below I create a new dataset for the songs that appeared in the UK and Germany
# Charts in the 2000s. I created a massive dataset for UK and Germany so I could
# see which songs, artists, and genres were most popular in the charts during
# this decade.

uk_charts_listing <- rbind(uk_2000_data,
                           uk2001_data,
                           uk2002_data,
                           uk2003_data,
                           uk2004_data,
                           uk2005_data,
                           uk2006_data,
                           uk2007_data,
                           uk2008_data,
                           uk2009_data,
                           uk2010_data)

ger_charts_listing <- rbind(ger2000_data,
                            ger2001_data,
                            ger2002_data,
                            ger2003_data,
                            ger2004_data,
                            ger2005_data,
                            ger2006_data,
                            ger2007_data,
                            ger2008_data,
                            ger2009_data,
                            ger2010_data)


# I added a year column to the charts listing dataframes so I could do yearly
# analysis if need be.

uk_charts_listing %<>%
  mutate(year = rep(2000:2010, each = 100))

ger_charts_listing %<>%
  mutate(year = rep(2000:2010, each = 100)) %>%
  rename(artist = X1,
         title = X2)


# This function is directly taken from Stack Overflow. User got documentation
# from toupper and used that to write out this function (or perhaps it's from
# the data itself?):
# https://stackoverflow.com/questions/6364783/capitalize-the-first-letter-of-both-words-in-a-two-word-string

simpleCap <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), substring(s, 2),
      sep="", collapse=" ")
}

# Here I count the number of times an artist, song, or genre has appeared in the
# UK/GER Charts and then get the top 10 or 20 for the decade. I had to count by
# lower-casing the target column (due to inconsistencies in capitilization), and
# then renaming the column and fixing the capitilization at the end. As
# mentioned above, the mutate and count lines were inspired by the StackOverflow
# post above.

yearly_uk_artists <- uk_charts_listing %>%
  count(tolower(artist)) %>%
  arrange(desc(n)) %>%
  rename(artist = `tolower(artist)`) %>%
  mutate(artist = sapply(artist, simpleCap)) %>%
  head(10)

yearly_uk_songs <- uk_charts_listing %>%
  group_by(artist) %>%
  count(tolower(title)) %>%
  arrange(desc(n)) %>%
  rename(title = `tolower(title)`) %>%
  mutate(title = sapply(title, simpleCap)) %>%
  head(10)

# For genres, it was a little bit different since the genre column was a list of
# characters. In order to analyze the genre data for the UK and Germany, I had
# to create an entirely new dataframe from the now-unlisted genre column and
# count the number of times a genre appeared in the charts.

yearly_uk_genres <- data.frame(table(unlist(strsplit(tolower(uk_charts$genre), ",")))) %>%
  arrange(desc(Freq)) %>%
  head(25)

yearly_ger_artists <- ger_charts_listing %>%
  mutate(artist = tolower(artist)) %>%
  count(artist) %>%
  arrange(desc(n)) %>%
  mutate(artist = sapply(artist, simpleCap)) %>%
  head(10)
  
yearly_ger_songs <- ger_charts_listing %>%
  group_by(artist) %>%
  mutate(title = tolower(title)) %>%
  count(title) %>%
  arrange(desc(n)) %>%
  mutate(title = sapply(title, simpleCap)) %>%
  head(10)

yearly_ger_genres <- data.frame(table(unlist(strsplit(tolower(ger_charts$genre), ",")))) %>%
  arrange(desc(Freq)) %>%
  head(25)

# Below are the top artists, genres, and songs gt tables for the UK and Germany.
# I created the gt table here mostly so I can practice on how the code would
# look like when I move it to the shinyapp. I did not end up putting this code
# in the shinyapp and have it be interactive with the user's input because I
# found it easier to just load the gt table and avoid any lag that might occur.

foruk_artists <- yearly_uk_artists %>%
  gt() %>%
  tab_header(title = "Artists that have Appeared the Most in UK Charts",
             subtitle = "Data from 2000 - 2010") %>%
  cols_label(artist = "Artist",
             n = "Count")

foruk_songs <- yearly_uk_songs %>%
  ungroup(artist) %>%
  gt() %>%
  tab_header(title = "Songs that have Appeared the Most in UK Charts",
             subtitle = "Data from 2000 - 2010") %>%
  cols_label(artist = "Artist",
             title = "Song Title",
             n = "Count")

foruk_genres <- yearly_uk_genres %>%
  gt() %>%
  tab_header(title = "Most Popular Genres in UK Charts",
             subtitle = "Data from 2000 - 2010") %>%
  cols_label(Var1 = "Genre",
             Freq = "Count") %>%
  tab_footnote("Most songs fall under multiple genres.",
               locations = cells_title(groups = "subtitle"))

forger_artists <- yearly_ger_artists %>%
  gt() %>%
  tab_header(title = "Artists that have Appeared the Most in German Charts",
             subtitle = "Data from 2000 - 2010") %>%
  cols_label(artist = "Artist",
             n = "Count")

forger_songs <- yearly_ger_songs %>%
  ungroup(artist) %>%
  gt() %>%
  tab_header(title = "Songs that have Appeared the Most in German Charts",
             subtitle = "Data from 2000 - 2010") %>%
  cols_label(artist = "Artist",
             title = "Song Title",
             n = "Count")

forger_genres <- yearly_ger_genres %>%
  gt() %>%
  tab_header(title = "Most Popular Genres in German Charts",
             subtitle = "Data from 2000 - 2010") %>%
  cols_label(Var1 = "Genre",
             Freq = "Count") %>%
  tab_footnote("Most songs fall under multiple genres.",
               locations = cells_title(groups = "subtitle"))


# Here I make the danceability, valence, energy, and tempo animated distribution
# plots for Germany and the UK over time. I instead have the gganimated plot
# here instead of on the shinyapp as I did originally because Mitchell suggested
# that I save the plots as gifs and just load it in the shiny app. This turned
# out to be a great idea because the shinyapp was able to load the animated
# plots quickly without any problem. If I had the following code on shiny and
# ran the app, the website would lag and would not load anything until the
# graphs were loaded (even the gt tables which were normally quick to load). If
# you to the very last chunk below, you can see the original ggplot unanimated
# plot and see that the code has not changed as much.

# PS: transition_states uses {closest_state} in order to display the year. I ran
# into a problem with this initially because I kept using {frame_time}.

uk_danceability <- uk_charts %>%
                ggplot(aes(danceability)) +
                geom_density(fill = "#faac0f", colour = "#fcab08", alpha = 0.7) +
                ggtitle("Danceability Distribution in UK Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

uk_valence <- uk_charts %>%
                ggplot(aes(valence)) +
                geom_density(fill = "#69b3a2", colour = "#e9ecef", alpha = 0.7) +
                ggtitle("Valence Distribution in UK Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

uk_tempo <- uk_charts %>%
                ggplot(aes(tempo)) +
                geom_density(fill = "#4287f5", colour = "#316fd4", alpha = 0.7) +
                transition_time(year) +
                labs(title = "Tempo Distribution in UK Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

uk_energy <- uk_charts %>%
                ggplot(aes(energy)) +
                geom_density(fill = "#f2493d", colour = "#f090e9", alpha = 0.7) +
                ggtitle("Energy Distribution in UK Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

ger_danceability <- ger_charts %>%
                ggplot(aes(danceability)) +
                geom_density(fill = "#faac0f", colour = "#fcab08", alpha = 0.7) +
                ggtitle("Danceability Distribution in Germany Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

ger_valence <- ger_charts %>%
                ggplot(aes(valence)) +
                geom_density(fill = "#69b3a2", colour = "#e9ecef", alpha = 0.7) +
                ggtitle("Valence Distribution in Germany Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

ger_tempo <- ger_charts %>%
                ggplot(aes(tempo)) +
                geom_density(fill = "#4287f5", colour = "#316fd4", alpha = 0.7) +
                transition_time(year) +
                labs(title = "Tempo Distribution in Germany Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

ger_energy <- ger_charts %>%
                ggplot(aes(energy)) +
                geom_density(fill = "#f2493d", colour = "#f090e9", alpha = 0.7) +
                ggtitle("Energy Distribution in Germany Charts {closest_state}") +
                theme_ipsum(base_family = "Calibri") +
                transition_states(year)

```

```{r word_cloud_maker, echo=FALSE}

# The UK and Germany cloud dataframes are created below. The dataframes list the
# number of times a genre appeared on the charts per year. I had to delete some
# of the data because Spotify was unable to find the genres for a few songs. I
# made sure to include the year variable in order to create a wordcloud for each
# year on shiny so users can see the most popular genres in the charts per year.

ukcloud <- uk_charts %>%
  separate_rows(genre, sep = ',') %>%
  group_by(genre = tolower(genre), year) %>%
  filter(!genre == "") %>%
  summarise(Count = n()) %>%
  ungroup(genre) %>%
  arrange(year)

gercloud <- ger_charts %>%
  separate_rows(genre, sep = ',') %>%
  group_by(genre = tolower(genre), year) %>%
  filter(!genre == "") %>%
  summarise(Count = n()) %>%
  ungroup(genre) %>%
  arrange(year)
```


```{r set_wd, echo=FALSE}

# I save the wordcloud dataframes, the audio features animated plots as gifs,
# and the uk and german charts data in the shiny apps directory so I can load it
# in shiny. There was a line of code that set the working directory to the app
# (using setwd), but I removed it since it was using a hard coded pathfile.

saveRDS(ukcloud, "ukcloud.rds")
saveRDS(gercloud, "gercloud.rds")

anim_save("uk_danceability.gif", animate(uk_danceability))
anim_save("uk_valence.gif", animate(uk_valence))
anim_save("uk_tempo.gif", animate(uk_tempo))
anim_save("uk_energy.gif", animate(uk_energy))
anim_save("ger_danceability.gif", animate(ger_danceability))
anim_save("ger_valence.gif", animate(ger_valence))
anim_save("ger_tempo.gif", animate(ger_tempo))
anim_save("ger_energy.gif", animate(ger_energy))


saveRDS(uk_charts, file = "uk_charts.rds")
saveRDS(ger_charts, file = "ger_charts.rds")
```

```{r unused_data, echo=FALSE}

# Here I store all the danceability, valence, and tempo features per year.
# Although this is no longer going to be used in the actual project, I am saving
# this code below because I feel like it would be nice to see what I did for
# this project whenever I look back on it. Yes, originally I did create 88
# different plots by hand to analyze the features of the songs in the German/UK
# charts per year. However, I later switched to an animated format, which still
# used the components of these ggplots but with transition states.

#danceability_uk_2000 <- uk2000_features %>%
#  ggplot(aes(danceability)) +
#  geom_density(fill = "#faac0f", colour = "#fcab08", alpha = 0.7) +
#  ggtitle("Danceability Distribution in UK Charts 2000") +
#  theme_ipsum(base_family = "Calibri")

#valence_uk_2000 <- uk2000_features %>%
#  ggplot(aes(valence)) +
#  geom_density(fill = "#69b3a2", colour = "#e9ecef", alpha = 0.7) +
#  ggtitle("Valence Distribution in UK Charts 2000") +
#  theme_ipsum(base_family = "Calibri") 

#tempo_uk_2000 <- uk2000_features %>%
#  ggplot(aes(tempo)) +
#  geom_density(fill = "#4287f5", colour = "#316fd4", alpha = 0.7) +
#  ggtitle("Tempo Distribution in UK Charts 2000") +
#  theme_ipsum(base_family = "Calibri")

#energy_uk_2000 <- uk2000_features %>%
#  ggplot(aes(energy)) +
#  geom_density(fill = "#f2493d", colour = "#f090e9", alpha = 0.7) +
#  ggtitle("Energy Distribution in UK Charts 2000") +
#  theme_ipsum(base_family = "Calibri")

```

# Data Gathered Thus Far
All data has been gathered and publshed on shiny!

# How did you get this fine piece of data?
Thank you for asking stranger. I got this data by scraping the list from this website: http://www.uk-charts.top-source.info/index.shtml. I will continue to get data from this website from 2000-2010 for the UK, then I will use https://www.offiziellecharts.de to get the data for Germany. 

# Why did you stop after 1 year?
This was mostly me just testing the waters of what I can do with the data I gathered. Obviously this isn't the final project, it's not even %5 of the final project. I still have to scrape 1,900 more songs, and probably bind all of the data into two big chunks of 10 years of observations for Germany and UK. However, I will have to figure out how to get Spotify to analyze the data in the "titles" section of the UK data (it currently returns a lot of NULL observations, so I will have to read more of the sportifyr documentation). I should have all the data I want by tomorrow, and I will have to figure out how to get spotify to read that data over the weekend so I can start making some nice looking graphs. Overall, I think I am pretty happy where I am with this project.

# Are you going to keep updating this repo?
Of course! Everything pushed after today is just me gathering data from the UK and Germany charts. Hopefully by Sunday I will have created two massive chunks of data, but that is if I can get the spotify function to work. It is crucial for me to do this because most of the spotify commands involving track analysis can only take 100 observations at once.

Here is the repo for your convenience:
https://github.com/NinthHeaven/milestone4


UPDATE: As of May 8th, 2020, this project has been completed and can be viewed below:
https://ninthheaven.shinyapps.io/UK_GER_Charts/

